working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
RESULTS

Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a positive statistically clear correlation for both markers (p<0.05). The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.

add phylogenetic signal of traits...

>>>>

Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a positive statistically clear correlation for both markers (p<0.05). The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25. The phylogenetic signal of traits was significantly correlated with pollen size, stigma measurements and style length (p<0.05). Although with a lack of a significant correlation pagel's lambda values were also relatively high (>0.45) for incompatibility index, ovary length and levels of selfing. Moreover, Mantel test between heterospecific pollen effect and traits gave also a positive significant correlation with a  r value of 0.4. When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect (LOOK AT HOW I EXPRESS THIS IS VERY RELEVANT, HP EFFECT FOR ME IS THE OPPOSITE)

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
RESULTS

Results of Mantel test between heterospecific pollen effect and
phylogenetic distance gave a positive statistically clear correlation
for both markers (p\textless{}0.05). The correlations with ITS and RBCL
markers was respectively of 0.29 and 0.25.

add phylogenetic signal of traits\ldots{}

>>>>

Results of Mantel test between heterospecific pollen effect and
phylogenetic distance gave a positive statistically clear correlation
for both markers (p\textless{}0.05). The correlations with ITS and RBCL
markers was respectively of 0.29 and 0.25. The phylogenetic signal of
traits was significantly correlated with pollen size, stigma
measurements and style length (p\textless{}0.05). Although with a lack
of a significant correlation pagel's lambda values were also relatively
high (\textgreater{}0.45) for incompatibility index, ovary length and
levels of selfing. Moreover, Mantel test between heterospecific pollen
effect and traits gave also a positive significant correlation with a r
value of 0.4. When the effect was look trait by trait with Mantel test,
stigma type and stigma measurements (length, width and area) gave a
significant positive correlation with heterospecific pollen effect (LOOK
AT HOW I EXPRESS THIS IS VERY RELEVANT, HP EFFECT FOR ME IS THE
OPPOSITE)
